### 2022-01-19 response2/response2.tex
Change res to q3

We would like to thank the reviewer for his/her insightful comments on the theoretical foundations of our model. Accordingly, we have been able to significantly refine our discussion on the underlying assumptions and corresponding physical conditions of our system. We hence believe that our response, and the corresponding changes we incorporated to the manuscript would be sufficient to clarify the issues raised.

@@

We agree with the reviewer that the issue was not addressed properly. Therefore, we have made an extensive discussion on the underlying validity of approximation in Eq.~[34]. Fisrt, we discuss about the complications we have to face when we are trying to derive a full description of a realistic periodically driven system. Later, we clarify the actual conditions and requirements to approximate a stationary particle distribution function for driven system.

The accessibility of coherent driving fields such as laser opens many interesting capabilities for manupulating quantum systems. This leads to Floquet engineeting of solid-state, atomic, and photonic systems with the basic of Floquet states. However, the powerful thermodynamic rules that related to the static systems in thermal equilibrium in general cannot be apply into the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}. Therefore, in order to achieve the viability of Floquet engineering in fermion systems, it is crucial to undestand the conditions for a steady state particle distribution and it is one of the major challenge in the field. Among previous studies on this topic, a main point of inestigation is time-scales. As an example, if the switch-on of the driving field is not far from the past, the distribution function of a qunatum system will highly depend on the switching-on protocal of the periodic driving \cite{dehghani2014}. Although we can consider the intermediate timescales, there would be many physical processes causing the heating of the quantum system. A variety of approches for stabilizing the quantum system under this condition has been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}. When the applied driving field get stronger the heating caused by the field gets increase. Thus, the cooloing system needs to be much stronger and this leads to a non-perturbative inclusion of the bath to the system. In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasiparticles and their scattering processes have addressed semi-classically using the Boltzmann approch. However, a fully microscopic description of heating of a driven system is a rather challenging task due to the multiple processes that need to be investigate.
It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging. In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}. This leads towards to a featureless state at long times. All these concludes that undestanding of heating processes in any timescale and adress them to describe relastic driven system needs the treatment of very rich physics. However, under proper parameter regimes to be discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.

@@

While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mentioned about the previous studies \cite{dini16,endo09} influence our work. In these studies the transport properties of quantum Hall syatems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
The main focus of the present study is to utilize the novel Floquet-Drude conductivity method \cite{wackerl20,wackerlthesis20} to describe dressed quantum Hall systems. Since it is required to compare our novel theoritical description of charge transport properties with the previous studies \cite{dini16,endo09} of dressed quantum Hall systems, we adopted the same assumptions and conditions used in previous studies. In addition, analysis of long-range needs the proper treatment of interections. These interactions are a different topic and these effects are not discussed in this work and left as future study.

>>>>

We would like to thank the reviewer for his/her insightful comments on the theoretical foundations of our model. Accordingly, we have been able to significantly refine our discussion on the underlying assumptions and corresponding physical conditions of our system. We hence believe that our response and the corresponding changes we incorporated into the manuscript would be sufficient to clarify the issues raised.

@@

We agree with the reviewer that the issue was not addressed properly. Therefore, we have made an extensive discussion on the underlying validity of approximation in Eq.~[34]. First, we discuss the complications we have to face when we are trying to derive a full description of a realistic periodically driven system. Later, we clarify the actual conditions and requirements to approximate a stationary particle distribution function for a driven system.

The accessibility of coherent driving fields such as laser opens many interesting capabilities for manipulating quantum systems. This leads to the Floquet engineering of solid-state, atomic, and photonic systems with the basics of Floquet states. In general, the powerful thermodynamic rules related to the static systems in thermal equilibrium, cannot be applied to the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}. Therefore, to achieve the viability of Floquet engineering in fermion systems, it is crucial to understand the conditions for a steady-state particle distribution and it is one of the main challenges in the field. Among previous studies on this topic, a major point of investigation is time scales. As an example, if the switch-on of the driving field is not far from the past, the distribution function of a quantum system will highly depend on the switching-on protocol of the periodic driving \cite{dehghani2014}. Although we can consider the intermediate timescales, there would be many physical processes causing the heating of the quantum system. A variety of approaches for stabilizing the quantum system under this condition have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}. When the applied driving field gets more powerful the heating caused by the field gets increases. Thus, the cooling system needs to be much stronger and this leads to a non-perturbative inclusion of the bath in the system. In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasiparticles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
> However, a fully microscopic description of heating of a driven system is a rather challenging task due to the multiple processes that need to be investigate.
It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging. In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}. This leads towards to a featureless state at long times. All these concludes that undestanding of heating processes in any timescale and adress them to describe relastic driven system needs the treatment of very rich physics. However, under proper parameter regimes to be discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.

@@

While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mentioned about the previous studies \cite{dini16,endo09} influence our work. In these studies the transport properties of quantum Hall syatems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
The main focus of the present study is to utilize the novel Floquet-Drude conductivity method \cite{wackerl20,wackerlthesis20} to describe dressed quantum Hall systems. Since it is required to compare our novel theoritical description of charge transport properties with the previous charge transport studies \cite{dini16,endo09} of quantum Hall systems, we adopted the same assumptions and conditions. In addition, Wackel \textit{et al.} \cite{wackerl20} have developed the Floquet-Drude conductivity theory through the short-range impurity potential assumptions.  Thus, first we need to improve  Floquet-Drude conductivity theory before use it on the dressed quantum Hall system. The analysis of the implications from long-range impurity potentials needs a proper treatment of high-order interections.
The discussion of these interactions through Floquet theory is a different topic. Thus, it is not discussed in this work. However, following the reviewer’s suggestion, we are planning to discuss these effects through our future study.
